Convex Surrogates via Polyhedral Losses

### 2019-02-01 cvx-fin.tex
TRIMming the appendix. Loving the puns.

\section{Considering unlabeled properties}
  Note that when $\Gamma$ is elicitable, there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.

  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.

\begin{lemma}\label{lem:trim-subsets-not-full-dimensional}
Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
\end{lemma}
\begin{proof}
  If there is a full-dimensional level set $\Gamma_u \subsetneq \Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for all $p \in \Gamma_u$.
%  (This is true because $\phi^{-1}(u) \neq \phi^{-1}(w)$ as the level sets are not equal.)
  However, closed, convex, full-dimensional level sets have positive Lebesgue measure in $\reals^{n-1}$,\jessiet{I don't know if we need a citation/proof for this assertion...} and thus contradicts the convexity of $G$, as convex functions are differentiable at all but a countable set of points.
  This in turn contradicts the elicitability of $\Gamma$, and so, we conclude that $\Gamma_u$ is not full-dimensional.
\end{proof}

\begin{lemma}\label{lem:unique-opt-on-inter}
  Let $\Gamma:\simplex \toto \R'$ be an elicitable property such that $\trim(\Gamma)$ is finite.
  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
\end{lemma}
\begin{proof}
\jessiet{Come back and formalize}
  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
  \bigskip
  \jessie{Formalization below}
  \hrule
  Consider that $\trim(\Gamma)$ is nonredundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior. \jessiet{Sanity check here?}
  Since $\Gamma$ is elicitable, the score $G$ must be convex.
  For $w \in \R'$, if $\Gamma_w \subseteq \Gamma_u$, then we contradict the nonredundancy of $\trim(\Gamma)$, so we only worry about the case where $\Gamma_w \not \subseteq \Gamma_u$..

  Suppose there is such a level set.
  There must be another level set $v$ so that $\Gamma_w \cap \inter{\Gamma_v}$ is nonempty, since level sets of elicitable properties are closed.
  Therefore, for $q \in \Gamma_w$, we observe $\Gamma(q) \subseteq \{u,w\}$ or $\{v,w\}$.
  More importantly- for $q \in \Gamma_w$, $\Gamma(q)$ is not constant.

  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $q' \in \Gamma_w \cap \inter{\Gamma_v}$.
  Additionally, $\conv(\{q,q'\}) \subseteq \Gamma_w$, and observe that $\conv(\{q,q'\})$ is not countable.
  Since there is a bijection from $\Gamma(p)$ to $\partial_p G(p)$, we then note that $|\partial_pG(p)| > 1$ on an uncountable set, and $\partial_p G(p)$ is not constant on $\conv(\{q,q'\})$.
  This contradicts the convexity of $G$, and in turn, the elicitability of $\Gamma$ and $\trim(\Gamma)$.

  Therefore, for all $p \in \inter{\Gamma_u}$, we must observe $\Gamma(p) = \{u\}$.

\end{proof}

\begin{corollary}\label{cor:cant-span-interiors}
  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
\end{corollary}
\jessiet{I can write something for a proof of this if you want, but it follows from the previous statement pretty quickly.}

\begin{lemma}\label{lem:trim-full-dim}
  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many full-dimensional level sets.
  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.
\end{lemma}
\begin{proof}
  Consider an arbitrary level set $\theta$.
  If $\theta$ is not full-dimensional, we want to show that it must be the intersection of some full-dimensional level sets in $\trim(\Gamma)$.\jessiet{Why?  Add more details about why the level set can't span two full-dimensional level sets}
  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.

  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
  It must then span the interior multiple level sets, as level sets of elicitable properties are closed.
  By Corollary~\ref{cor:cant-span-interiors}, we contradict the elicitability of $\Gamma$.
  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$.
  As trimming a property removes such redundant reports, we then observe that $\theta \not \in \trim(\Gamma)$.
  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
\end{proof}

>>>>

%% Jessie commented out 1/31/19 because of the updated proof to the trim TFAE, these are now no longer necessary.
%%\section{Considering unlabeled properties}
%%  Note that when $\Gamma$ is elicitable, there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
%%  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
%%  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.
%%
%%  The next two proofs take advantage of this duality correspondence between the subgradients of the convex score $G$ of an elicitable property and the property values.
%%
%%
%%\begin{lemma}\label{lem:trim-subsets-not-full-dimensional}
%%Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
%%For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
%%\end{lemma}
%%\begin{proof}
%%  If there is a full-dimensional level set $\Gamma_u \subsetneq \Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for all $p \in \Gamma_u$.
%%%  (This is true because $\phi^{-1}(u) \neq \phi^{-1}(w)$ as the level sets are not equal.)
%%  However, closed, convex, full-dimensional level sets have positive Lebesgue measure in $\reals^{n-1}$,\jessiet{I don't know if we need a citation/proof for this assertion...} and thus contradicts the convexity of $G$, as convex functions are differentiable at all but a countable set of points.
%%  This in turn contradicts the elicitability of $\Gamma$, and so, we conclude that $\Gamma_u$ is not full-dimensional.
%%\end{proof}
%%
%%\begin{lemma}\label{lem:unique-opt-on-inter}
%%  Let $\Gamma:\simplex \toto \R'$ be an elicitable property such that $\trim(\Gamma)$ is finite.
%%  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
%%\end{lemma}
%%\begin{proof}
%%\jessiet{Come back and formalize}
%%  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
%%  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
%%  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
%%  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
%%  \bigskip
%%  \jessie{Formalization below}
%%  \hrule
%%  Consider that $\trim(\Gamma)$ is nonredundant, and $p \in \inter{\Gamma_u}$ only if $\Gamma_u \in \trim(\Gamma)$ by Lemma~\ref{lem:trim-full-dim}, as a closed, convex set is full-dimensional if and only if it has nonempty interior. \jessiet{Sanity check here?}
%%  Since $\Gamma$ is elicitable, the score $G$ must be convex.
%%  For $w \in \R'$, if $\Gamma_w \subseteq \Gamma_u$, then we contradict the nonredundancy of $\trim(\Gamma)$, so we only worry about the case where $\Gamma_w \not \subseteq \Gamma_u$..
%%
%%  Suppose there is such a level set.
%%  There must be another level set $v$ so that $\Gamma_w \cap \inter{\Gamma_v}$ is nonempty, since level sets of elicitable properties are closed.
%%  Therefore, for $q \in \Gamma_w$, we observe $\Gamma(q) \subseteq \{u,w\}$ or $\{v,w\}$.
%%  More importantly- for $q \in \Gamma_w$, $\Gamma(q)$ is not constant.
%%
%%  Let's say there is a $q \in \Gamma_w \cap \inter{\Gamma_u}$ and $q' \in \Gamma_w \cap \inter{\Gamma_v}$.
%%  Additionally, $\conv(\{q,q'\}) \subseteq \Gamma_w$, and observe that $\conv(\{q,q'\})$ is not countable.
%%  Since there is a bijection from $\Gamma(p)$ to $\partial_p G(p)$, we then note that $|\partial_pG(p)| > 1$ on an uncountable set, and $\partial_p G(p)$ is not constant on $\conv(\{q,q'\})$.
%%  This contradicts the convexity of $G$, and in turn, the elicitability of $\Gamma$ and $\trim(\Gamma)$.
%%
%%  Therefore, for all $p \in \inter{\Gamma_u}$, we must observe $\Gamma(p) = \{u\}$.
%%
%%\end{proof}
%%
%%\begin{corollary}\label{cor:cant-span-interiors}
%%  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
%%  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$ with $u \neq v$.
%%\end{corollary}
%%\jessiet{I can write something for a proof of this if you want, but it follows from the previous statement pretty quickly.}
%%
%%\begin{lemma}\label{lem:trim-full-dim}
%%  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many full-dimensional level sets.
%%  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.
%%\end{lemma}
%%\begin{proof}
%%  Consider an arbitrary level set $\theta$.
%%  If $\theta$ is not full-dimensional, we want to show that it must be the intersection of some full-dimensional level sets in $\trim(\Gamma)$.\jessiet{Why?  Add more details about why the level set can't span two full-dimensional level sets}
%%  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.
%%
%%  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
%%  It must then span the interior multiple level sets, as level sets of elicitable properties are closed.
%%  By Corollary~\ref{cor:cant-span-interiors}, we contradict the elicitability of $\Gamma$.
%%  Thus, any $\theta$ that is not full-dimensional must be the intersection of a finite set of full-dimensional level sets $\theta_i \in \trim(\Gamma)$.
%%  As trimming a property removes such redundant reports, we then observe that $\theta \not \in \trim(\Gamma)$.
%%  Therefore, each $\theta \in \trim(\Gamma)$ must be full-dimensional.
%%\end{proof}
